G85R Analysis: TKT Signaling Pathway

### 2024-11-06 TKT_RNAseq/R Code/TKT Signaling Pathway.Rmd
pca

---
title: "G85R Analysis: Rescue Response"
author: "John Santiago"
date: "2024-09-18"
output: html_document
---

@@

library(plotly)
library(edgeR)
library(heatmaply)
library(org.Dm.eg.db)
library(KEGGREST)
library(RcisTarget)
library(DT)
##source('/Users/johncsantiago/Documents/GitHub/WhartonLab/GOandKEGGPlottingFunctions.R')
library(VennDiagram)

@@

enzyme2KEGG = as.list(org.Dm.egENZYME2EG)

@@

## Response Genes in G85R relative to WT

@@

x = "GRxWT.FC"
y = "GRxWT.MC"

mean.data = G85R.meancpm[, c('WT.F', 'WT.M',
                             'GR.F', 'GR.M')]
main.title = "G85R vs WT: Female and Male DE Genes"

##RG = Response Genes
GRxWT.RG = TKT.biplot(x, y, mean.data, main.title)

GRxWT.RG[[1]]

@@

##Sample titles as strings. Only fill in up to your number of selected categories
set1 = "Female Increased"
set2 = "Female Decreased"
set3 = "Male Increased"
set4 = "Male Decreased"

##items to be compared (ex: gene names) as a 1 dimensional vectors. Only give inputs up to your number of selected categories
s1 = GRxWT.RG[[2]][GRxWT.RG[[2]][,'FDR1'] <= 0.05 &
                   GRxWT.RG[[2]][,'FC1'] > 0, "FBgn"]
s2 = GRxWT.RG[[2]][GRxWT.RG[[2]][,'FDR1'] <= 0.05 &
                   GRxWT.RG[[2]][,'FC1'] < 0, "FBgn"]
s3 = GRxWT.RG[[2]][GRxWT.RG[[2]][,'FDR2'] <= 0.05 &
                   GRxWT.RG[[2]][,'FC2'] > 0, "FBgn"]
s4 = GRxWT.RG[[2]][GRxWT.RG[[2]][,'FDR2'] <= 0.05 &
                   GRxWT.RG[[2]][,'FC2'] < 0, "FBgn"]

NormalResponse = data.frame(Female = c(length(s2), length(s1)),
                            Male =  c(length(s4), length(s3)))
row.names(NormalResponse) = c("Decreased", "Increased")
NormalResponse = as.matrix(NormalResponse)

par(mar = c(2,4,2,7.5))
barplot(NormalResponse,
        beside = T,
        ylab = "Total DEGs",
        main = "G85R vs Silent",
        col = c('navy', 'firebrick'),
        angle = c(45, 45, 315, 315), density = 50,
        legend.text = c("Decreased", "Increased"),
        args.legend = list(x = 8,
                           y = 700,
                           bty = 'n'))
#legend(x = 6.25, 
#       y = 700, 
#       legend = c("Increased", "Decreased"),
#       pt.bg = c('grey35', 'lightgrey'),
#       xpd = T, 
#       bty = "o",
#       pch = 22,
#       pt.cex = 1.5)

@@

##Sample titles as strings. Only fill in up to your number of selected categories
set3 = "Female Increased"
set1 = "Female Decreased"
set4 = "Male Increased"
set2 = "Male Decreased"

##items to be compared (ex: gene names) as a 1 dimensional vectors. Only give inputs up to your number of selected categories
s3 = GRxWT.RG[[2]][GRxWT.RG[[2]][,'FDR1'] <= 0.05 &
                   GRxWT.RG[[2]][,'FC1'] > 0, "FBgn"]
s1 = GRxWT.RG[[2]][GRxWT.RG[[2]][,'FDR1'] <= 0.05 &
                   GRxWT.RG[[2]][,'FC1'] < 0, "FBgn"]
s4 = GRxWT.RG[[2]][GRxWT.RG[[2]][,'FDR2'] <= 0.05 &
                   GRxWT.RG[[2]][,'FC2'] > 0, "FBgn"]
s2 = GRxWT.RG[[2]][GRxWT.RG[[2]][,'FDR2'] <= 0.05 &
                   GRxWT.RG[[2]][,'FC2'] < 0, "FBgn"]

main = ""

grid.newpage()
tempvenn=draw.quad.venn(area1=length(s1),area2=length(s2),area3=length(s3),area4=length(s4), n12=length(intersect(s1,s2)),n13 = length(intersect(s1,s3)),n14 = length(intersect(s1,s4)),n23 = length(intersect(s2,s3)),n24 = length(intersect(s2,s4)),n34 = length(intersect(s3,s4)),n123 =  length(intersect(s1,intersect(s2,s3))),n124 =  length(intersect(s1,intersect(s2,s4))), n134 = length(intersect(s1,intersect(s3,s4))),n234 = length(intersect(s2,intersect(s3,s4))),n1234 = length(intersect(s1,intersect(s2,intersect(s3,s4)))),category =c(set1,set2,set3,set4),fill = c("navy", "darkgreen","gold","firebrick"),cex=2,cat.cex = 1, title = "main")

@@

##Female and Male Shared DEGs
```{r echo = F, include = F}

s1 = GRxWT.RG[[2]][GRxWT.RG[[2]][,'FDR1'] <= 0.05 &
                   GRxWT.RG[[2]][,'FC1'] > 0, "FBgn"]
s2 = GRxWT.RG[[2]][GRxWT.RG[[2]][,'FDR1'] <= 0.05 &
                   GRxWT.RG[[2]][,'FC1'] < 0, "FBgn"]
s3 = GRxWT.RG[[2]][GRxWT.RG[[2]][,'FDR2'] <= 0.05 &
                   GRxWT.RG[[2]][,'FC2'] > 0, "FBgn"]
s4 = GRxWT.RG[[2]][GRxWT.RG[[2]][,'FDR2'] <= 0.05 &
                   GRxWT.RG[[2]][,'FC2'] < 0, "FBgn"]

MF.shared.DEGs = c(intersect(s1,s3), intersect(s2,s4))

bg = row.names(TKT.EdgeR)
GRWTMF.Enr = Subset.Enrichment(bg, MF.shared.DEGs)

@@

RTCC.GRWTMF = tree(GRWTMF.Enr, "CC")
treemapPlot(RTCC.GRWTMF)

RTCC.GRWTMF = tree(GRWTMF.Enr, "BP")
treemapPlot(RTCC.GRWTMF)

RTCC.GRWTMF = tree(GRWTMF.Enr, "MF")
treemapPlot(RTCC.GRWTMF)

cat.data = GRWTMF.Enr
GO.ontology = "CC"
FC = setNames(GRxWT.RG[[2]][, "FC1"], row.names(GRxWT.RG[[2]]))
FDR = setNames(GRxWT.RG[[2]][, "FDR1"], row.names(GRxWT.RG[[2]]))
usecats = "sigs.only"
sigs = MF.shared.DEGs

reversal.GO20(cat.data, GO.ontology, FC, FDR, usecats, sigs)

cat.data = GRWTMF.Enr
GO.ontology = "BP"
FC = setNames(GRxWT.RG[[2]][, "FC1"], row.names(GRxWT.RG[[2]]))
FDR = setNames(GRxWT.RG[[2]][, "FDR1"], row.names(GRxWT.RG[[2]]))
usecats = c(1:39)
sigs = MF.shared.DEGs

reversal.GO20(cat.data, GO.ontology, FC, FDR, usecats, sigs)

cat.data = GRWTMF.Enr
GO.ontology = "MF"
FC = setNames(GRxWT.RG[[2]][, "FC1"], row.names(GRxWT.RG[[2]]))
FDR = setNames(GRxWT.RG[[2]][, "FDR1"], row.names(GRxWT.RG[[2]]))
usecats = c(1:30)
sigs = MF.shared.DEGs

reversal.GO20(cat.data, GO.ontology, FC, FDR, usecats, sigs)

##Female Only DEGs
```{r echo = F, include = F}

F.only.DEGs = c(setdiff(GRxWT.RG[[2]][GRxWT.RG[[2]][,'FDR1'] <= 0.05, "FBgn"],
                        GRxWT.RG[[2]][GRxWT.RG[[2]][,'FDR2'] <= 0.05, "FBgn"]))

bg = row.names(TKT.EdgeR)
GRWTFonly.Enr = Subset.Enrichment(bg, F.only.DEGs)

RTCC.GRWTFonly = tree(GRWTFonly.Enr, "CC")
treemapPlot(RTCC.GRWTFonly)

RTCC.GRWTFonly = tree(GRWTFonly.Enr, "BP")
treemapPlot(RTCC.GRWTFonly)

RTCC.GRWTFonly = tree(GRWTFonly.Enr, "MF")
treemapPlot(RTCC.GRWTFonly)
```

cat.data = GRWTFonly.Enr
GO.ontology = "CC"
FC = setNames(GRxWT.RG[[2]][, "FC1"], row.names(GRxWT.RG[[2]]))
FDR = setNames(GRxWT.RG[[2]][, "FDR1"], row.names(GRxWT.RG[[2]]))
usecats = "sigs.only"
sigs = F.only.DEGs

reversal.GO20(cat.data, GO.ontology, FC, FDR, usecats, sigs)

cat.data = GRWTFonly.Enr
GO.ontology = "BP"
FC = setNames(GRxWT.RG[[2]][, "FC1"], row.names(GRxWT.RG[[2]]))
FDR = setNames(GRxWT.RG[[2]][, "FDR1"], row.names(GRxWT.RG[[2]]))
usecats = "sigs.only"
sigs = F.only.DEGs

reversal.GO20(cat.data, GO.ontology, FC, FDR, usecats, sigs)

cat.data = GRWTFonly.Enr
GO.ontology = "MF"
FC = setNames(GRxWT.RG[[2]][, "FC1"], row.names(GRxWT.RG[[2]]))
FDR = setNames(GRxWT.RG[[2]][, "FDR1"], row.names(GRxWT.RG[[2]]))
usecats = "sigs.only"
sigs = F.only.DEGs

reversal.GO20(cat.data, GO.ontology, FC, FDR, usecats, sigs)

##Male Only DEGs
```{r echo = F, include = F}

M.only.DEGs = c(setdiff(GRxWT.RG[[2]][GRxWT.RG[[2]][,'FDR2'] <= 0.05, "FBgn"],
                        GRxWT.RG[[2]][GRxWT.RG[[2]][,'FDR1'] <= 0.05, "FBgn"]))

bg = row.names(TKT.EdgeR)
GRWTMonly.Enr = Subset.Enrichment(bg, M.only.DEGs)
```

RTCC.GRWTMonly = tree(GRWTMonly.Enr, "CC")
treemapPlot(RTCC.GRWTMonly)

RTCC.GRWTMonly = tree(GRWTMonly.Enr, "BP")
treemapPlot(RTCC.GRWTMonly)

RTCC.GRWTMonly = tree(GRWTMonly.Enr, "MF")
treemapPlot(RTCC.GRWTMonly)

cat.data = GRWTMonly.Enr
GO.ontology = "CC"
FC = setNames(GRxWT.RG[[2]][, "FC2"], row.names(GRxWT.RG[[2]]))
FDR = setNames(GRxWT.RG[[2]][, "FDR2"], row.names(GRxWT.RG[[2]]))
usecats = c(1:28)
sigs = M.only.DEGs

reversal.GO20(cat.data, GO.ontology, FC, FDR, usecats, sigs)

cat.data = GRWTMonly.Enr
GO.ontology = "BP"
FC = setNames(GRxWT.RG[[2]][, "FC2"], row.names(GRxWT.RG[[2]]))
FDR = setNames(GRxWT.RG[[2]][, "FDR2"], row.names(GRxWT.RG[[2]]))
usecats = c(1:50)
sigs = M.only.DEGs

reversal.GO20(cat.data, GO.ontology, FC, FDR, usecats, sigs)

cat.data = GRWTMonly.Enr
GO.ontology = "MF"
FC = setNames(GRxWT.RG[[2]][, "FC2"], row.names(GRxWT.RG[[2]]))
FDR = setNames(GRxWT.RG[[2]][, "FDR2"], row.names(GRxWT.RG[[2]]))
usecats = c(1:50)
sigs = M.only.DEGs

reversal.GO20(cat.data, GO.ontology, FC, FDR, usecats, sigs)

##Sample titles as strings. Only fill in up to your number of selected categories
set1 = "Female"
set2 = "Male"

##items to be compared (ex: gene names) as a 1 dimensional vectors. Only give inputs up to your number of selected categories
s1 = GRWTFonly.Enr$GO[GRWTFonly.Enr$GO$adjp <= 0.05, "term"]
s2 = GRWTMonly.Enr$GO[GRWTMonly.Enr$GO$adjp <= 0.05, "term"]

main = ""

grid.newpage()
tempvenn=draw.pairwise.venn(area1 = length(s1),
                            area2 = length(s2),
                            cross.area = length(intersect(s1,s2)),
                            fill = c("blue", "red"),
                            cex = 2,
                            cat.cex = 1,
                            category = c(set1, set2),
                            title = "main")

```{r echo = F, include = F}

data("motifAnnotations_dmel_v9")
motifRankings = importRankings("/Users/johncsantiago/Documents/GitHub/WhartonLab/TKT_RNAseq/DataFiles/dm6_v10_clust.genes_vs_motifs.rankings.feather")
motifAnnotations = motifAnnotations_dmel_v9

##motif rankings table for every TF
motif.data = getRanking(motifRankings)
##motifs associated with a TF
##TF.data = motifAnnotations[motifAnnotations$TF == 'Tudor-SN',]
###TF.data = motifAnnotations[motifAnnotations$TF == 'Mad',]

##TF.motif.data = motif.data[motif.data$motifs %in% TF.data$motif,]

##Motif collection data directory
motif.collection.dir = "/Users/johncsantiago/Documents/GitHub/WhartonLab/DrosophilaMotifsSingletonData/"

##geneLists = GeneIDKey[MF.shared.DEGs, 'Symbol']
geneLists = GeneIDKey[F.only.DEGs, 'Symbol']
geneLists = GeneIDKey[M.only.DEGs, 'Symbol']

motifEnrichmentTable_wGenes <- cisTarget(geneLists, 
         motifRankings,
         motifAnnot=motifAnnotations)

motifs_AUC <- calcAUC(geneLists, motifRankings, nCores=1)

auc <- getAUC(motifs_AUC)
hist(auc, xlab="dAUC histogram",
     breaks=100, col="#ff000050", border="darkred")
nes3 <- (3*sd(auc)) + mean(auc)
abline(v=nes3, col="red")

motifEnrichmentTable <- addMotifAnnotation(motifs_AUC, nesThreshold=3,
     motifAnnot=motifAnnotations)

motifEnrichmentTable_wGenes <- addSignificantGenes(motifEnrichmentTable,
                      rankings=motifRankings, 
                      geneSets=geneLists)
dim(motifEnrichmentTable_wGenes)

resultsSubset <- motifEnrichmentTable_wGenes

showLogo(resultsSubset)

```{r echo = F, include = F}

anotatedTfs <- lapply(split(motifEnrichmentTable_wGenes$TF_highConf,
                            motifEnrichmentTable$geneSet),
                      function(x) {
                        genes <- gsub(" \\(.*\\). ", "; ", x, fixed=FALSE)
                        genesSplit <- unique(unlist(strsplit(genes, "; ")))
                        return(genesSplit)
                        })

anotatedTfs$hypoxia

##comparisons
primary = 'GRxWT.C'

x = 'GRxWT.C'

mean.data = mean.metab[, c('GR', 'WT')]

min.expression = 0

##Reversal pattern
FC.data = metab.FC[, c(primary)]
FC.data = na.omit(FC.data)

##Sig cutoff. Currently, at least 1 significant change
sig.metab = metab.FDR[metab.FDR[,primary]  < .05, ]
sig.metab = na.omit(sig.metab)
sig.metab = row.names(sig.metab)

FC.data = metab.FC[sig.metab, c(x)]
FDR.data = metab.FDR[sig.metab, c(x)]
mean.data = mean.data[sig.metab, ]

data = data.frame(Metab = sig.metab,
                  compoundID = KEGG.Key[sig.metab],
                  FDR = -log2(FDR.data),
                  FC = FC.data,
                  Color = 'grey',
                  size = 1,
                  Variable1.mean = mean.data[,1],
                  Control1.mean = mean.data[,2])

sig.metabs = data

main.title = "G85R Metabolites"

  data$Color[data$FC < 0] = 'royalblue'
  data$Color[data$FC > 0] = 'firebrick' 
  #data$Color[data$Symbol == "Arc1"] = 'gold'
  data$size = log10(apply(mean.data[,c(1,2)], 1, max))
  data$size[data$size<3] = 1

  data = na.omit(data)
  data = data[data$size > log2(min.expression),]
  data$size = data$size

  fig = plot_ly(data = data,
                x = ~FC,
                y = ~FDR,
                type = 'scatter',
                mode = 'markers',
                marker = list(color = ~Color,
                              colors = ~Color,
                              line = list(color = "black", width = 1.5),
                              size = ~size),
                hoverinfo = "text",
                hovertext = paste("Metabolite:", data$Metab,
                                  "\n Compound ID:", data$compoundID,
                                  "\n ", x, "p: ", round(2^-data$FDR, 2),
                                  "\n ", x, "FC: ", round(data$FC, 2),
                                  "\n ", colnames(mean.data)[1], "mean: ", signif(data$Variable1,2),
                                  "\n ", colnames(mean.data)[2], "mean: ", signif(data$Control1,2)))

  fig = fig %>% layout(title = main.title,
                       xaxis = list(title = paste(x, "FC")),
                       yaxis = list(title = paste(x, "-log2(p-value)")),
                       showlegend = F)

CompoundData = sig.metabs[1,]

x = 'GRxWT.C'
y = 'GRxWT.C'

mean.data = mean.metab[, c('GR', 'WT')]

Fx = 'GRxWT.FC'
My = 'GRxWT.MC'

Fmean = G85R.meancpm[, c('GR.F', 'WT.F')]
Mmean = G85R.meancpm[, c('GR.M', 'WT.M')]

compoundandgenes(CompoundData, x, y, mean.data, Fx, My, Fmean, Mmean)

CompoundData = sig.metabs[2,]

x = 'GRxWT.C'
y = 'GRxWT.C'

mean.data = mean.metab[, c('GR', 'WT')]

Fx = 'GRxWT.FC'
My = 'GRxWT.MC'

Fmean = G85R.meancpm[, c('GR.F', 'WT.F')]
Mmean = G85R.meancpm[, c('GR.M', 'WT.M')]

compoundandgenes(CompoundData, x, y, mean.data, Fx, My, Fmean, Mmean)

CompoundData = sig.metabs[3,]

x = 'GRxWT.C'
y = 'GRxWT.C'

mean.data = mean.metab[, c('GR', 'WT')]

Fx = 'GRxWT.FC'
My = 'GRxWT.MC'

Fmean = G85R.meancpm[, c('GR.F', 'WT.F')]
Mmean = G85R.meancpm[, c('GR.M', 'WT.M')]

compoundandgenes(CompoundData, x, y, mean.data, Fx, My, Fmean, Mmean)

CompoundData = sig.metabs[4,]

x = 'GRxWT.C'
y = 'GRxWT.C'

mean.data = mean.metab[, c('GR', 'WT')]

Fx = 'GRxWT.FC'
My = 'GRxWT.MC'

Fmean = G85R.meancpm[, c('GR.F', 'WT.F')]
Mmean = G85R.meancpm[, c('GR.M', 'WT.M')]

compoundandgenes(CompoundData, x, y, mean.data, Fx, My, Fmean, Mmean)

CompoundData = sig.metabs[5,]

x = 'GRxWT.C'
y = 'GRxWT.C'

mean.data = mean.metab[, c('GR', 'WT')]

Fx = 'GRxWT.FC'
My = 'GRxWT.MC'

Fmean = G85R.meancpm[, c('GR.F', 'WT.F')]
Mmean = G85R.meancpm[, c('GR.M', 'WT.M')]

compoundandgenes(CompoundData, x, y, mean.data, Fx, My, Fmean, Mmean)

CompoundData = sig.metabs[41,]

x = 'GRxWT.C'
y = 'GRxWT.C'

mean.data = mean.metab[, c('GR', 'WT')]

Fx = 'GRxWT.FC'
My = 'GRxWT.MC'

Fmean = G85R.meancpm[, c('GR.F', 'WT.F')]
Mmean = G85R.meancpm[, c('GR.M', 'WT.M')]

compoundandgenes(CompoundData, x, y, mean.data, Fx, My, Fmean, Mmean)

##  Are there genes that respond to rescue in Silent and G85R for both sexes?

##  TKT-Df Response
```{r echo = F}

x = "GRF.CxDf"
y = "WTF.CxDf"

mean.data = G85R.meancpm[, c('GR.F', 'WT.F',
                             'TktDfGR.F', 'TktDfWT.F')]
main.title = "Female TKT-Df DE Genes"

##RG = Response Genes
FDf.RG = TKT.biplot(x, y, mean.data, main.title)

FDf.RG[[1]]

x = "GRM.CxDf"
y = "WTM.CxDf"

mean.data = G85R.meancpm[, c('GR.M', 'WT.M',
                             'TktDfGR.M', 'TktDfWT.M')]
main.title = "Male TKT-Df DE Genes"

##RG = Response Genes
MDf.RG = TKT.biplot(x, y, mean.data, main.title)

MDf.RG[[1]]

x = "GRF.CxDf"
y = "GRM.CxDf"

mean.data = G85R.meancpm[, c('GR.F', 'GR.M',
                             'TktDfGR.F', 'TktDfGR.M')]
main.title = "G85R TKT-Df DE Genes"

##RG = Response Genes
GRDf.RG = TKT.biplot(x, y, mean.data, main.title)

GRDf.RG[[1]]

x = "WTF.CxDf"
y = "WTM.CxDf"

mean.data = G85R.meancpm[, c('WT.F', 'WT.M',
                             'TktDfWT.F', 'TktDfWT.M')]
main.title = "Silent TKT-Df DE Genes"

##RG = Response Genes
WTDf.RG = TKT.biplot(x, y, mean.data, main.title)

WTDf.RG[[1]]

##Sample titles as strings. Only fill in up to your number of selected categories
set1 = "Silent Female Df"
set2 = "Silent Male Df"
set3 = "G85R Female Df"
set4 = "G85R Male Df"

##items to be compared (ex: gene names) as a 1 dimensional vectors. Only give inputs up to your number of selected categories
s1 = FDf.RG[[2]][FDf.RG[[2]][,'FDR2'] <= 0.05, "FBgn"]
s2 = MDf.RG[[2]][MDf.RG[[2]][,'FDR2'] <= 0.05, "FBgn"]
s3 = FDf.RG[[2]][FDf.RG[[2]][,'FDR1'] <= 0.05, "FBgn"]
s4 = MDf.RG[[2]][MDf.RG[[2]][,'FDR1'] <= 0.05, "FBgn"]

NormalResponse = data.frame(Rescue = c(set1, set2, set3, set4),
                            TotalGenes =  c(length(s1), length(s2), length(s3), length(s4)))

fig <- plot_ly(data = NormalResponse, x = ~Rescue, y = ~TotalGenes, type = 'bar', name = 'Normal Response',
               marker = list(color = 'lightgrey',
                      line = list(color = 'rgb(8,48,107)',
                                  width = 3)))
fig <- fig %>% layout(yaxis = list(title = 'Total Response Genes (Control vs TKT-Df'))

##Sample titles as strings. Only fill in up to your number of selected categories
set1 = "Silent Female Df"
set2 = "Silent Male Df"
set3 = "G85R Female Df"
set4 = "G85R Male Df"

##items to be compared (ex: gene names) as a 1 dimensional vectors. Only give inputs up to your number of selected categories
s1 = FDf.RG[[2]][FDf.RG[[2]][,'FDR2'] <= 0.05, "FBgn"]
s2 = MDf.RG[[2]][MDf.RG[[2]][,'FDR2'] <= 0.05, "FBgn"]
s3 = FDf.RG[[2]][FDf.RG[[2]][,'FDR1'] <= 0.05, "FBgn"]
s4 = MDf.RG[[2]][MDf.RG[[2]][,'FDR1'] <= 0.05, "FBgn"]

main = ""

grid.newpage()
tempvenn=draw.quad.venn(area1=length(s1),area2=length(s2),area3=length(s3),area4=length(s4), n12=length(intersect(s1,s2)),n13 = length(intersect(s1,s3)),n14 = length(intersect(s1,s4)),n23 = length(intersect(s2,s3)),n24 = length(intersect(s2,s4)),n34 = length(intersect(s3,s4)),n123 =  length(intersect(s1,intersect(s2,s3))),n124 =  length(intersect(s1,intersect(s2,s4))), n134 = length(intersect(s1,intersect(s3,s4))),n234 = length(intersect(s2,intersect(s3,s4))),n1234 = length(intersect(s1,intersect(s2,intersect(s3,s4)))),category =c(set1,set2,set3,set4),fill = c("blue", "red","green","yellow"),cex=2,cat.cex = 1, title = "main")

##WTF.C vs WTF.TKT-Df
```{r echo = F, include = F}

bg = row.names(TKT.EdgeR)
WTF.Df.Enr = Subset.Enrichment(bg, FDf.RG[[2]][FDf.RG[[2]][,'FDR2'] <= 0.05, "FBgn"])

RTCC.WTF.Df = tree(WTF.Df.Enr, "CC")
treemapPlot(RTCC.WTF.Df)

RTBP.WTF.Df = tree(WTF.Df.Enr, "BP")
treemapPlot(RTBP.WTF.Df)

RTMF.WTF.Df = tree(WTF.Df.Enr, "MF")
treemapPlot(RTMF.WTF.Df)

##WTM.C vs WTM.TKT-Df
```{r echo = F, include = F}

>>>>

---
title: "G85R Analysis: TKT Signaling Pathway"
author: "John Santiago"
date: "2024-09-18"
output: html_document
---

@@

library(plotly)
library(edgeR)
library(heatmaply)
library(org.Dm.eg.db)
library(KEGGREST)
library(RcisTarget)
library(DT)
source('/Users/johncsantiago/Documents/GitHub/WhartonLab/GOandKEGGPlottingFunctions.R')
library(VennDiagram)

@@

enzyme2KEGG = as.list(org.Dm.egENZYME2EG)
enzyme2KEGG$'3.6.1.77' = "35231"
enzyme2KEGG = enzyme2KEGG[names(enzyme2KEGG) != "`3.6.1.-`"]

@@

@@

#TKT = FBgn0036784

FBgn = "FBgn0036784"
Name = GeneIDKey[FBgn, "Symbol"]
TKT = GeneIDKey[FBgn, "Name"]
enzymeID = names(enzyme2KEGG)[grep(TKT, enzyme2KEGG)]
reactions <- keggGet(c(enzymeID))

temp.substrate = reactions[[1]]["SUBSTRATE"][[1]]
temp.substrate = strsplit(temp.substrate, split = ":")
substrates = c(1:length(temp.substrate))
i=1
while(i<=length(temp.substrate)){
  substrates[i] = substring(temp.substrate[[i]][2], 1,6)
  names(substrates)[i] = substring(temp.substrate[[i]][1], 1, (nchar(temp.substrate[[i]][1]) - 4))
  i=i+1
}

temp.product = reactions[[1]]["PRODUCT"][[1]]
temp.product = strsplit(temp.product, split = ":")
products = c(1:length(temp.product))
i=1
while(i<=length(temp.product)){
  products[i] = substring(temp.product[[i]][2], 1,6)
  names(products)[i] = substring(temp.product[[i]][1], 1, (nchar(temp.product[[i]][1]) - 4))
  i=i+1
}

TKTmap = data.frame(from.Name = c(names(substrates), rep(Name, length(products))),
                    from.ID = c(substrates, rep(TKT, length(products))),
                    to.Name = c(rep(Name, length(substrates)), names(products)),
                    to.ID = c(rep(TKT, length(substrates)), products))

secondary = c(substrates, products)

secondary.enzymes = as.character()

i=1
while( i<= length(secondary)){
  temp.enzymes = keggGet(secondary[i])[[1]]["ENZYME"][[1]]
  temp.enzymes = unlist(enzyme2KEGG[intersect(temp.enzymes, names(enzyme2KEGG))])
  secondary.enzymes = c(secondary.enzymes, temp.enzymes)
  i = i +1
}

secondary.enzymes = unique(secondary.enzymes)

secondary.enzymes = row.names(GeneIDKey[GeneIDKey$Name %in% unlist(secondary.enzymes),])

tertiary.enzymes = as.character()

j = 1

while(j <= length(secondary.enzymes)){
  FBgn = secondary.enzymes[j]
  Name = GeneIDKey[FBgn, "Symbol"]
  ID = GeneIDKey[FBgn, "Name"]
  enzymeID = names(enzyme2KEGG)[grep(ID, enzyme2KEGG)]
  reactions <- keggGet(c(enzymeID))

  temp.substrate = reactions[[1]]["SUBSTRATE"][[1]]
  temp.substrate = strsplit(temp.substrate, split = ":")
  substrates = c(1:length(temp.substrate))
  i=1
  while(i<=length(temp.substrate)){
    substrates[i] = substring(temp.substrate[[i]][2], 1,6)
    names(substrates)[i] = substring(temp.substrate[[i]][1], 1,
                                     (nchar(temp.substrate[[i]][1]) - 4))
    i=i+1
  }

  temp.product = reactions[[1]]["PRODUCT"][[1]]
  temp.product = strsplit(temp.product, split = ":")
  products = c(1:length(temp.product))
  i=1
  while(i<=length(temp.product)){
    products[i] = substring(temp.product[[i]][2], 1,6)
    names(products)[i] = substring(temp.product[[i]][1], 1, (nchar(temp.product[[i]][1]) - 4))
    i=i+1
  }

  temp.map = data.frame(from.Name = c(names(substrates), rep(Name, length(products))),
                        from.ID = c(substrates, rep(ID, length(products))),
                        to.Name = c(rep(Name, length(substrates)), names(products)),
                        to.ID = c(rep(ID, length(substrates)), products))
  row.names(temp.map) =  1:nrow(temp.map)
  TKTmap = rbind(TKTmap, temp.map)
  tertiary.enzymes = c(tertiary.enzymes, substrates, products)

  j=j+1
  }

@@

visedges = TKTmap[, c("from.Name", "to.Name")]
colnames(visedges) = c("from", "to")

temp = colorRampPalette(c('royalblue',"dodgerblue",'red', "firebrick"))(401)

visedges$color = round(TKT.EdgeR.FC[purine.path$FBgn, comparison.T],2)
##visedges$width = .5 + abs(visedges$color)
visedges$color[visedges$color < (-2)] = -2
visedges$color[visedges$color > (2)] = 2
visedges$color = (visedges$color * 100) +201
visedges$color = temp[visedges$color]
visedges$symbol = GeneIDKey[visedges$FBgn, 'Symbol']
visedges$fdr = signif(TKT.EdgeR[visedges$FBgn, comparison.T], 2)
visedges$GR = round(mean.cpm[visedges$FBgn, cond1],1)
visedges$WT = round(mean.cpm[visedges$FBgn, cond2],1)
visedges$width = .01 + (1*abs(log10(visedges$WT)))

groups = setNames(c(TKTmap$from.ID, TKTmap$to.ID),
                  c(TKTmap$from.Name, TKTmap$to.Name))
groups[substr(groups, 1,1) == "C"] = "metabolite"
groups[groups != "metabolite"] = "enzyme"
groups['CG8036'] = "TKT"

nodes = data.frame(id = unique(c(TKTmap$from.Name, TKTmap$to.Name)),
                   label = unique(c(TKTmap$from.Name, TKTmap$to.Name)),
                   group = groups[unique(c(TKTmap$from.Name, TKTmap$to.Name))])

nodes$label[nodes$label == "CG8036"] = "TKT"

nodes$color = round(TKT.EdgeR.FC[p, comparison.T],2)
##visedges$width = .5 + abs(visedges$color)
visedges$color[visedges$color < (-2)] = -2
visedges$color[visedges$color > (2)] = 2
visedges$color = (visedges$color * 100) +201
visedges$color = temp[visedges$color]
visedges$symbol = GeneIDKey[visedges$FBgn, 'Symbol']
visedges$fdr = signif(TKT.EdgeR[visedges$FBgn, comparison.T], 2)
visedges$GR = round(mean.cpm[visedges$FBgn, cond1],1)
visedges$WT = round(mean.cpm[visedges$FBgn, cond2],1)
visedges$width = .01 + (1*abs(log10(visedges$WT)))

visNetwork(nodes,visedges)%>%
  visOptions(highlightNearest = TRUE, nodesIdSelection = TRUE)%>%
  #visEdges(arrows = visedges$arrows)#%>%
  visGroups(groupname = "metabolite", 
            shape = 'box', color = "gold",
            physics=T, size = 25, 
            font=list(color="black"))%>%
  visGroups(groupname = "TKT", 
            shape = 'circle', color = "firebrick",
            physics=F, size = 25, 
            font=list(color="white"))

@@

```{r}

PPP = keggGet('dme00030')[[1]]
PPP.enz = PPP$GENE
PPP.met = PPP$COMPOUND

download.kegg(pathway.id = "00030",
              species = "dme",
              kegg.dir = "/Users/johncsantiago/Documents/GitHub/WhartonLab/TKT_RNAseq/R Code/")

node.data = node.info('/Users/johncsantiago/Documents/GitHub/WhartonLab/TKT_RNAseq/R Code/dme00030.xml')

node.info = data.frame(ID = unlist(node.data$kegg.names, use.names = F),
                       number = rep(names(node.data$kegg.names),
                                    lengths(node.data$kegg.names)),
                       x = 0,
                       y = 0,
                       color = 0,
                       names = "")
node.info$x = node.data$x[node.info$number]
node.info$y = node.data$y[node.info$number]

node.info = node.info[grep("C", node.info$ID),]
node.info = node.info[grep("CG", node.info$ID, invert = T),]

enzymes = as.character()

i=1
while( i<= nrow(node.info)){
  temp.enzymes = keggGet(node.info$ID[i])[[1]]["ENZYME"][[1]]
  temp.enzymes = unlist(enzyme2KEGG[intersect(temp.enzymes, names(enzyme2KEGG))])
  enzymes = c(enzymes, temp.enzymes)
  i = i +1
}

edges = data.frame(from.Name = as.character(),
                   from.ID = as.character(),
                   to.Name = as.character(),
                   to.ID = as.character())

j = 1

while(j <= length(enzymes)){
  FBgn = na.omit(GeneIDKey[GeneIDKey$Name == enzymes[j], "FBgn"])
  Name = GeneIDKey[FBgn, "Symbol"]
  ID = GeneIDKey[FBgn, "Name"]
  enzymeID = names(enzymes)[i]
  reactions <- keggGet(c(enzymeID))

  temp.substrate = reactions[[1]]["SUBSTRATE"][[1]]
  temp.substrate = strsplit(temp.substrate, split = ":")
  substrates = c(1:length(temp.substrate))
  i=1
  while(i<=length(temp.substrate)){
    substrates[i] = substring(temp.substrate[[i]][2], 1,6)
    names(substrates)[i] = substring(temp.substrate[[i]][1], 1,
                                     (nchar(temp.substrate[[i]][1]) - 4))
    i=i+1
  }

  temp.product = reactions[[1]]["PRODUCT"][[1]]
  temp.product = strsplit(temp.product, split = ":")
  products = c(1:length(temp.product))
  i=1
  while(i<=length(temp.product)){
    products[i] = substring(temp.product[[i]][2], 1,6)
    names(products)[i] = substring(temp.product[[i]][1], 1, (nchar(temp.product[[i]][1]) - 4))
    i=i+1
  }

  temp.edges = data.frame(from.Name = c(names(substrates), rep(Name, length(products))),
                          from.ID = c(substrates, rep(ID, length(products))),
                          to.Name = c(rep(Name, length(substrates)), names(products)),
                          to.ID = c(rep(ID, length(substrates)), products))
  row.names(temp.edges) =  1:nrow(temp.edges)
  edges = rbind(edges, temp.edges)
  j=j+1
  }

edges = unique(edges)

edges = rbind(edges[edges$from.ID %in% node.info$ID, ],
              edges[edges$to.ID %in% node.info$ID, ])

@@

```{r}

visedges = edges[, c("from.Name", "to.Name")]
colnames(visedges) = c("from", "to")

nodes = data.frame(id = unique(node.info$ID))

visNetwork(nodes,visedges)

@@
